\newpage

\begin{thebibliography}{25}

\bibitem{artin}
Michael Artin, \emph{Algebra}, Prentice Hall of India, New Delhi 2007

\bibitem{berardi}
Luigia Berardi, \emph{Algebra e teoria dei codici correttori}, Franco angeli
Editore 1994.

 \bibitem{berkelamp}
E.R. Berkelamp, \emph{Factoring Polynomials over Finite Fileds},
The Bell System Technical Journal, October 1967, pag. 1853-1859.

 \bibitem{blahut}
Richard E. Blahut, \emph{Theory and Practice of Error Control Codes},
Addison Wesley publishing Company, 1984.

\bibitem{blake}
Ian F. Blake, Ronald C. Mullin, \emph{The Mathematical Theory of Coding},
Academic Press 1975.

%\bibitem{bose}
%R.C. Bose, D.K. Ray-Chaudhuri, \emph{On A Class of Error Correcting Binary Group Codes}, Information and Control march 1960 pag. 68–79.

% \bibitem{borges}
% Jorge Luis Borges, \emph{L'Aleph},
% Feltrinelli 2008, traduzione di Francesco Montalto, prima edizione 1952.

\bibitem{cattaneo}
Giulia Maria Piacentini Cattaneo, \emph{Algebra, un approccio algoritmico},
Zanichelli 2007, prima ed. 1996.

\bibitem{cantor}
D.G. Cantor, H. Zasenhaus, \emph{A new Algorithm for Factoring Polynomials over Finite Fileds},
Mathematics of Computation, volume 36, numero 154, aprile 1981, pag. 587-592.


 \bibitem{cerruti}
 U. Cerruti, F. Vaccarino \emph{From Cyclotomic Extensions to Generalized
 Ramanuyan's Sum through the Winograd Transform}, pre-print.

\bibitem{cherung}
K.M. CHerung, F. Pollara \emph{Phobos Lander Coding System: Software and Analysis},
TDA progess report, April-June 1988, pag 274-286.



\bibitem{childs}
Lindsday N. Childs, \emph{A Concrete Introduction to Higher Algebra},
Springer-Verlag Gmbh, Third Edition 2009.

\bibitem{davis}
Philip J. Davis, \emph{Circulant Matrices},
John Wiley and Sons, 1979.

\bibitem{difebbraro}
Angela Di Febbraro, Alessandro Giua, \emph{Sistemi ad eventi discreti},
McGraw Hill, ed 2011, prima ed 2002.

%\bibitem{gorenstein}
%D.C Gorenstein, N. Zierler, \emph{A Class of Error Correcting Codes in $p^m$ symbols}, J. Soc. Indust. Appl. Math. 1961, num. 9, pag. 207-214.


%\bibitem{hocquenghem}
%A. Hocquenghem, \emph{Codes correcteurs d'erreurs}, Chiffres, pag 147–156, September 1959



\bibitem{herstein}
I.N. Herstein, \emph{Algebra},
editori riuniti, University Press 2010, prima ed. 1982.

\bibitem{jacobson}
Nathan Jacobson, \emph{Basic Algebra I}, W.H. Freeman and Company, prima ed. 1985.

\bibitem{kosh}
Thomas Koshy, \emph{Elementary Number Theory with applications}, Accademic Press, Elzevier, 2007.

\bibitem{languasco}
A. Languasco, A. Zaccagnini, \emph{Introduzione alla crittografia}, Ulrico Hoepli editore 2004.

\bibitem{lidl}
R. Lidl, H. Niederreiter \emph{Introduction to Finite Fields and Applications},
Cambridge university press 1994, prima edizione 1986.

\bibitem{lint}
J.H. van Lint, \emph{Introduction to Coding Theory},
Springer-Verlag, GTM 86 Third Edition 1999.

\bibitem{milne}
J.S. Milne, \emph{Fields and Galois Theory}, electronic version,
Creative
Commons license, 27 May 1998.
\begin{verbatim}
http://www.jmilne.org/math/
\end{verbatim}

\bibitem{murphy}
Timothy Murphy, \emph{Course 373, Finite Fields}, electronic version, Creative Commons license.
\begin{verbatim}
pet.ece.iisc.ernet.in/sathish/FiniteFields.pdf
\end{verbatim}

\bibitem{montabone}
Andrea Montabone, \emph{Matrici Circolanti ed Applicazioni},
Tesi di Laurea Magistrale, Università degli studi di Torino, Ottobre 2011.
Relatore: Prof. U. Cerruti.

\bibitem{miller}
R. L. Miller, T. K. Truong e I. S. Reed, \emph{Efficient Program for decoding the $(255,223)$ Reed-Solomon Code over $GF(2^{8})$}, IEEE num. $127$ $1980$ pag $136$-$142$.

\bibitem{perrin}
Daniel Perrin, \emph{Algebraic Geometry, an introduction}, Springer 2008.

\bibitem{sloane}
F.J. MacWilliams, N.J.A. Sloane, \emph{The Theory of Error-Correcting Codes},
North Holland Publishing company 1977.

\bibitem{shannon}
Claude E. Shannon, \emph{A Mathematica Theory of Comunication},
Bell System Technical Journal 27 379-423, July/October 1948.

\bibitem{shoup}
Victor Shoup, \emph{A Computational Introduction to Number Theory and Algebra},
electronic version, Creative Commons license, 2008, version 2.
\begin{verbatim}
http://shoup.net/ntb/
\end{verbatim}

\bibitem{sivarama}
R. Sivaramakrishnan, \emph{Classical Theory of Arithmetic Functions},
Taylor and Francis, 1989.

\bibitem{stoka}
M. Stoka, \emph{Corso di Geometria},
CEDAM, 1995.

\bibitem{wynjones}
Alun Wyn-jones, \emph{Circulants}, no editor: electronic version, Creative
Commons license, January 2008.
\begin{verbatim}
http://www.circulants.org/circ/
\end{verbatim}

\bibitem{winograd}
S. Winograd, \emph{Arithmetic Complexity of Computations}, SIAM 1980.

\bibitem{winograd2}
S. Winograd, \emph{On Computing the Discrete Fourier Transform}, Mathematics of Computation, Vol. $32$, Num. $141$, Gennaio $1978$, pag. $175$-$199$.

\end{thebibliography}




